---
title: "People-centric Restoration: Assigning Different Land Tenures based on Land Uses"
author: "Pooja Choksi"
date: "2022-06-03"
output: html_document
--

# LAND USE-BASED TENURE ASSINGMENTS FOR INDIAN VILLAGES

This dataset has been created using the Census 2011 land use records. The resords have been assigned tenures based on commonly accepted de jure land tenure regimes across India. 

We retrieved land use records from Census 2011(https://censusindia.gov.in/2011census/dchb/DCHB.html) for every district in the states and Union territories of India (As this data is owned by the Government of India, we are unable to share the datasheets downloaded from this website and used in this analaysis)x. We manually created csv files for each district within each state once we downloaded them from the website. From the data downloaded, For each village with a census code, the columns we selected are:
1. Total population 
2. Total number of households 
3. Total area in hectares
4. Land-use data (with a total of ten categories of land uses included) 

Land use categories in Census 2011: 
1. Forest 
2. Area under non-agricultural use 
3. Barren or uncultivable land 
4. Permanent pastures or grazing lands
5. Land under misc tree crops (orchards)
6. Culturable Wasteland
7. Fallow lands other than current fallow
8. Current fallow land 
9. Net Sown Area
10. Total irrigated land 
11. Total unirrigated land 

In the following code chunk, we combine and clean all the data from individual districts to create one country wide land use dataset. Refer to methods section 'Data sources and preparation' for more details. 

```{r include = FALSE}

library(data.table)
library(dplyr)
library(tidyr)
library(htmltools)
library(rmarkdown)
library(stringr)
library(ggplot2)

```

Combine all the sepeare district datasheets from the census website into one csv 

```{r message = FALSE, warning = FALSE}


#Combining data from all the states
dat.summary.original = sapply(list.files(path="C:\\Users\\pooja\\Documents\\GitHub\\Land-Tenure-Restoration-Potential\\Land-Tenure-Restoration-Potential\\Census2011-landUse-CSVFiles\\Sheets_For_Analysis",recursive=T, #looping through each subfolder for state
  pattern="_Census2011_LandUse.csv",full.names=T), function(file) {df = read.csv(file, stringsAsFactors=FALSE, colClasses=c(Village_name= "character",
                              Census_Code = "character",
                              District_Name = "character",
                              Subdistrict_Block="character",
                              Total_Population = "integer",
                              Total_Household= "integer",
                              Total_area_in_hectares="numeric",
                              forests_land ="numeric",
                              non_agricultural_land="numeric",
                              barren_uncultivable_land="numeric",
                              pasture_grazing_land="numeric",
                              misc_tree_crop_land="numeric",
                              culturable_wasteland="numeric",
                              fallow_other_than_current_fallow_land= "numeric",
                              current_fallow_land="numeric",
                              net_sown_area="numeric",
                              total_irrigated_land="numeric",
                              total_unirrigated_land="numeric",
                              State ="character"), header=TRUE)})

#Combine all rows 
dat.summary = bind_rows(dat.summary.original)

```

Clean issues due to formatting in the original dataset

```{r include = FALSE}

#Issue with the village name column 
colnames(dat.summary)
dat.summary = dat.summary%>%mutate(Village_name = coalesce(Village_name, ï..Village_name))

#dat.summary = dat.summary%>%mutate(Village_name = coalesce(Village_name, Ã...Village_name))

#Remove extra rows (numbering issue)
dat.summary = subset(dat.summary, select = -c(X, ï..Village_name))

#drop any empty rows
filter_1 = dat.summary%>%filter(Village_name == "")
dat.summary = anti_join(dat.summary, filter_1)

#State names may differ due to spaces etc 
dat.summary = dat.summary%>%dplyr::mutate(State = recode(State, 
                                                         "Arunachal_Pradesh" = "Arunachal Pradesh", 
                                                         "karnataka" = "Karnataka",
                                                         "Madhya_Pradesh  " = "Madhya Pradesh",
                                                         "Madya Pradesh " = "Madhya Pradesh",
                                                         "Madhya Pradesh " = "Madhya Pradesh",
                                                         "Uttar_Pradesh" = "Uttar Pradesh", 
                                                         "Uttar Pradesh " = "Uttar Pradesh"))

unique(dat.summary$State)
#you should have 35 unique states and UT

#there is an error in Basti district - the state should be Uttar Pradesh, but the csv says Odisha
dat.summary = within(dat.summary, State[District_Name %in% c("Basti")]<-"Uttar Pradesh")

#Remove any possible duplicates due to copying errors in manual extraction of land use data
duplicates = dat.summary[duplicated(dat.summary$Census_Code), ]
dat.summary = anti_join(dat.summary, duplicates)

```

CLEANING TOTAL ALND AREA RELATED INCONSISTENCIES IN THE DATA

In the following chunk of code, we deal with the incosistencies in the data such as the difference in totals of all land uses and the reported total area of a village in hectares. Refer to methods section 'Data sources and preparation' for more details. 

```{r message = FALSE, warning = FALSE}

#First, we find mismatch in total hectares of land
##Is total hectares reported in the district datasheet = total of all land use categories?

#a. total up the land uses categories 
dat.summary = dat.summary %>%
  mutate(Total_land_uses = select(., forests_land:net_sown_area) %>% rowSums(na.rm = TRUE))

#b. check if total_hectares from census data match the total of land uses calculated in (a)
dat.summary = dat.summary%>%mutate(Totals_Match = 
                                     case_when(Total_area_in_hectares == Total_land_uses ~ "Match",TRUE~ "No_Match"))

#c. check if the match is > 2 hectares (we allow for 2 hectare difference due to rounding off and differences in int and num values across diff subdistricts/districts/states)
dat.summary = dat.summary%>%mutate(Difference_in_totals = Total_area_in_hectares- Total_land_uses)

#d. create column of 'unaccounted' land in records 
dat.summary = dat.summary%>%mutate(Unaccounted_hectares_in_records =
                                     case_when(Difference_in_totals>0 ~ Difference_in_totals, TRUE ~ 0))


#d. Determine which total area to use under different conditions (Refer to Table 3 in the Methods section for more information on the different conditions mentioned below) 
dat.summary = dat.summary%>%mutate(Total_hectares_for_prop = case_when(
  #if village didn't report total, use total of land uses
  (Total_area_in_hectares == 0 & Total_land_uses>0)~ (Total_land_uses+Unaccounted_hectares_in_records), 
  #if village total land use is greater than total area reported
  (Total_area_in_hectares< Total_land_uses)~ (Total_land_uses+Unaccounted_hectares_in_records),
  #allow 2 hectares of a difference in totals due to rounding off/diff method of addition
  (Difference_in_totals < -2) ~ (Total_land_uses+Unaccounted_hectares_in_records), 
  #Total_area_in_hectares != Total_land_uses ~Total_land_uses, 
  TRUE~ Total_area_in_hectares))

#Round all numeric data to 3 digits 
dat.summary = dat.summary %>% 
  mutate(across(where(is.numeric), ~ round(., digits = 3)))

```

CREATE FINAL DATASET FOR ANALYSIS

In this chunk of code we calculate proportion of land tenures in each village. We do so after we remove state-owned forests, uninhabited villages, villages with zero population. 

We dealt with these 4 types of villages in the census data in the following manner: 

1. State-owned forests:
As state owned land also receive census codes, we filtered out as many types of state owned land categories, including firing ranges, forest ranges as possible to remove from this analysis. 

2. Un-inhabited villages:
We filtered villages which were labelled ‘uninhabited’ by the Census of 2011. 

3. Zero population villages:
We have considered villages with a population of zero, as they have land use records. We assume that these villages are either un-inhabited as they are farm land or other land use owned by neighbouring villages or the Census 2011 enumerators were unable to reach them. As these villages have a land-use record, we considered them in our analysis. Below are the states in which we found villages with zero population. 

4. No Land use information:
There were som villages where no information on the land uses was provided. We had to remove these districts. 

With all the data that remained, we calculated the total number of hectares in each category of land tenure- common non-forest land, common forest land, individual land, unaccounted land tenure.

```{r message = FALSE, warning = FALSE}

#####1. Forest blocks#####
forest_village_name = dat.summary%>%filter(str_detect(Village_name, "Beat| Block|Forest|Camp| Reserve | Range | Gate| K.M.| Department"))
dat.summary = anti_join(dat.summary, forest_village_name)

forest_block = dat.summary%>%filter(str_detect(Subdistrict_Block, "Beat| Block|Forest|Camp| Reserve | Range | Gate| K.M."))
dat.summary = anti_join(dat.summary, forest_block)

forest_district = dat.summary%>%filter(str_detect(District_Name, "Beat| Block|Forest|Camp| Reserve | Range | Gate| K.M."))
#none of the disticts are forests

#####2/3. Uninhabited and zero population villages#####
#Filter all files with total population zero
population_zero = dat.summary%>%filter(Total_Population == 0)
uninhabited_village = dat.summary%>%filter(str_detect(Village_name, "Un-inhabited"))

dat.summary = anti_join(dat.summary, population_zero)
dat.summary = anti_join(dat.summary, uninhabited_village)

#####4. No land use data#####
no_landuse_data = dat.summary%>%filter(Total_hectares_for_prop == 0)
dat.summary = anti_join(dat.summary, no_landuse_data)

#Total number of hectares of different de jure land tenures 
dat.summary = dat.summary %>% dplyr::mutate(Total_Indiv = (net_sown_area+ current_fallow_land+ fallow_other_than_current_fallow_land), 
Total_Common = (non_agricultural_land+ barren_uncultivable_land+ pasture_grazing_land+ misc_tree_crop_land+ culturable_wasteland), 
                                     Total_Forest = forests_land,
                                     Total_Unaccounted = Unaccounted_hectares_in_records)

#Proportion of de jure land tenures
dat.summary = dat.summary %>% dplyr::mutate(Prop_Indiv = ((net_sown_area+ current_fallow_land+ fallow_other_than_current_fallow_land)/Total_hectares_for_prop)*100,  Prop_Common = ((non_agricultural_land+ barren_uncultivable_land+ pasture_grazing_land+ misc_tree_crop_land+ culturable_wasteland)/Total_hectares_for_prop)*100, 
Prop_Forest = (forests_land/Total_hectares_for_prop)*100,
                                     Prop_Unaccounted = (Unaccounted_hectares_in_records/Total_hectares_for_prop)*100)

#Round all numeric data to 3 digits 
dat.summary = dat.summary %>% 
  mutate(across(where(is.numeric), ~ round(., digits = 3)))
  
```

Before creating the final dataset clean the datasheet.

```{r message=FALSE, warning=FALSE,include = TRUE}
#There is a spelling mistake in some district names

#Recode district names which have minor formatting errors such as spaces before or after a distrcit name
dat.summary = dat.summary%>%dplyr::mutate(District_Name = recode(District_Name, 
                                                     "Ragarh " = "Rajgarh",
                                                     "Rajgarh " = "Rajgarh",
                                                     "Indore " = "Indore",
                                                     "Sehore " = "Sehore",
                                                     "Barwani " = "Barwani",
                                                     "Papum Pare" = "Papumpare"))


#Change some districts from Andhra to Telangana since they now fall in the newly created state (post 2011 census) 
dat.summary = dat.summary%>%mutate(State = case_when(District_Name == 
                                                 "Adilabad"~ "Telangana",
District_Name == "Karimnagar" ~ "Telangana",
District_Name ==  "Khammam"~"Telangana",
District_Name =="Mahbubnagar"~ "Telangana",
District_Name =="Medak"~ "Telangana",
District_Name =="Nalgonda"~"Telangana",
District_Name =="Nizamabad"~ "Telangana",
District_Name =="Rangareddy"~ "Telangana",
District_Name =="Warangal"~"Telangana",
TRUE ~ State))

```

#Save csv for use in script 02

```{r include = FALSE}

write.csv(dat.summary, "All-State-LandUse-Combined.csv")

```
