---
title: "People-centric restoration: Merging avaiable census village level spatial data with Census 2011 and 2001 codes for data matching"
author: "Pooja Choksi"
date: '2022-06-07'
output: html_document
---

DATA PREPARATION TO COMBINE SPATIAL AND LAND USE DATA

```{r setup, include=FALSE}

library(data.table)
library(dplyr)
library(tidyr)
library(sf)
library(rgdal)
library(tools)
library(sp)
```

In this chunk of code, we combine spatial data from WRIS and census2011 and 2001 codes. We do this becauase spatial data has 2001 codes and land use data is 2011 codes.

Spatial data source: SEDAC (https://sedac.ciesin.columbia.edu/data/set/india-india-village-level-geospatial-socio-econ-1991-2001/data-download)


```{r message = FALSE, warning= FALSE, include=TRUE, echo=FALSE}

#Load all the data

pathname = "C:\\Users\\pooja\\Documents\\GitHub\\Land-Tenure-Restoration-Potential\\Land-Tenure-Restoration-Potential\\Census2011-Original-BOundaries-From-Benjamin-data"

allstates <-list.files(pathname,pattern = "Census2011-Original-Boundaries.shp")

for (i in 1:length(allstates)) {
  varName <- paste0(basename(allstates)[i])
  assign(varName, readOGR(dsn = allstates[i]))
}

#Census codes include codes for State, dist, subdist, village for 2001 and 2011
#by merging the 2001 codes, we assign the 2011 codes to all the spatial files 

census_code_combined <- read.csv("Census-2001-2011-Codes-Combined.csv", 
                                 header = T, stringsAsFactors = FALSE,
                                 quote = '\"', colClasses = c('character','character', 'character',
                                                              'character', 'character', 
                                                              'factor','character', 'character',
                                                              'character', 'character', 
                                                              'factor' ))

```

In this chunk of code, we combine the spatial data and the census codes, so that we can eventually combine the land use data to the spatial files. We merge each state separately, instead of automating the process due to small differences in 'vill_code' in each of the state spatial files.

```{r message = FALSE, warning= FALSE, include=TRUE, echo=FALSE}

#2001 census codes are the same for all the states. This is because they used chronological numbers instead of the st, dist, subdist code

#1. AndhraPradesh
Andra_Pradesh <- sp::merge(`Andhra-Pradesh-Census2011-Original-Boundaries.shp`, census_code_combined, by.x = c("sid","vill_code", "did", "tid"), 
                    by.y = c("St_Code_2001","Vill_Code_2001", 
                             "Dst_Code_2001", "SubDist_Code_2001"),
                    duplicateGeoms = T)

#2. Assam
Assam <- sp::merge(`Assam-Census2011-Original-Boundaries.shp`, census_code_combined, by.x = c("sid","vill_code", "did", "tid"), 
                           by.y = c("St_Code_2001","Vill_Code_2001", 
                                    "Dst_Code_2001", "SubDist_Code_2001"),
                           duplicateGeoms = T)

#3. Bihar 
Bihar <- sp::merge(`Bihar-Census2011-Original-Boundaries.shp`, census_code_combined, by.x = c("sid","vill_code", "did", "tid"), 
                   by.y = c("St_Code_2001","Vill_Code_2001", 
                            "Dst_Code_2001", "SubDist_Code_2001"),
                   duplicateGeoms = T)

#4. Gujarat
Gujarat <- sp::merge(`Gujarat-Census2011-Boundaries.shp`, census_code_combined, by.x = c("sid","vill_code", "did", "tid"), 
                     by.y = c("St_Code_2001","Vill_Code_2001", 
                              "Dst_Code_2001", "SubDist_Code_2001"),
                     duplicateGeoms = T)

#5. Haryana
Haryana <- sp::merge(`Haryana-Census2011-Boundaries.shp`, census_code_combined, by.x = c("sid","vill_code", "did", "tid"), 
                     by.y = c("St_Code_2001","Vill_Code_2001", 
                              "Dst_Code_2001", "SubDist_Code_2001"),
                     duplicateGeoms = T)

#6. Himachal Pradesh
Himachal_Pradesh <- sp::merge(`Himachal-Pradesh-Census2011-Boundaries.shp`, census_code_combined, by.x = c("sid","vill_code", "did", "tid"), 
                                      by.y = c("St_Code_2001","Vill_Code_2001", 
                                               "Dst_Code_2001", "SubDist_Code_2001"),
                                      duplicateGeoms = T)

#7. Jammu- Kashmir
Jammu_Kashmir<- sp::merge(`Jammu-Kashmir-Census2011-Boundaries.shp`, census_code_combined, by.x = c("sid","vill_code", "did", "tid"), 
                       by.y = c("St_Code_2001","Vill_Code_2001", 
                                "Dst_Code_2001", "SubDist_Code_2001"),
                       duplicateGeoms = T)

#8. Jharkhand
Jharkhand<- sp::merge(`Jharkhand-Census2011-Boundaries.shp`, census_code_combined, by.x = c("sid","vill_code", "did", "tid"), 
                      by.y = c("St_Code_2001","Vill_Code_2001", 
                               "Dst_Code_2001", "SubDist_Code_2001"),
                      duplicateGeoms = T)

#9 Karnataka
Karnataka<-  sp::merge(`Karnataka-Census2011-Original-Boundaries.shp`, census_code_combined, by.x = c("sid","vill_code", "did", "tid"), 
                    by.y = c("St_Code_2001","Vill_Code_2001", 
                             "Dst_Code_2001", "SubDist_Code_2001"),
                    duplicateGeoms = T)

#10. Kerala
Kerala <-  sp::merge(`Kerala-Census2011-Original-BOundaries.shp`, census_code_combined, by.x = c("sid","vill_code", "did", "tid"), 
                     by.y = c("St_Code_2001","Vill_Code_2001", 
                              "Dst_Code_2001", "SubDist_Code_2001"),
                     duplicateGeoms = T)

#11. Odisha
Odisha <-  sp::merge(`Odisha-Census2011-Original-Boundaries.shp`, census_code_combined, by.x = c("sid","vill_code", "did", "tid"), 
                     by.y = c("St_Code_2001","Vill_Code_2001", 
                              "Dst_Code_2001", "SubDist_Code_2001"),
                     duplicateGeoms = T)

#12. Punjab
Punjab <-  sp::merge(`Punjab-Census2011-Boundaries.shp`, census_code_combined, by.x = c("sid","vill_code", "did", "tid"), 
                     by.y = c("St_Code_2001","Vill_Code_2001", 
                              "Dst_Code_2001", "SubDist_Code_2001"),
                     duplicateGeoms = T)

#13. Rajasthan
Rajashthan <-  sp::merge(`Rajasthan-Census2011-Boundaries.shp`, census_code_combined, by.x = c("sid","vill_code", "did", "tid"), 
                         by.y = c("St_Code_2001","Vill_Code_2001", 
                                  "Dst_Code_2001", "SubDist_Code_2001"),
                         duplicateGeoms = T)

#14. Sikkim
Sikkim <- sp::merge(`Sikkim-Census2011-Original-Boundaries.shp`, census_code_combined, by.x = c("sid","vill_code", "did", "tid"), 
                            by.y = c("St_Code_2001","Vill_Code_2001", 
                                     "Dst_Code_2001", "SubDist_Code_2001"),
                            duplicateGeoms = T)

#15. Tamil Nadu
Tamil_Nadu <- sp::merge(`Tamil-Nadu-Census2011-Boundaries.shp`, census_code_combined, by.x = c("sid","vill_code", "did", "tid"), 
                                by.y = c("St_Code_2001","Vill_Code_2001", 
                                         "Dst_Code_2001", "SubDist_Code_2001"),
                                duplicateGeoms = T)

#17 Telangana
Telangana <- sp::merge(`Telangana-Census2011-Original-Boundaries.shp`, census_code_combined, by.x = c("sid","vill_code", "did", "tid"), 
                     by.y = c("St_Code_2001","Vill_Code_2001", 
                              "Dst_Code_2001", "SubDist_Code_2001"),
                     duplicateGeoms = T)

#18. Tripura
Tripura <- sp::merge(`Tripura-Census2011-Original-Boundaries.shp`, census_code_combined, by.x = c("sid","vill_code", "did", "tid"), 
                             by.y = c("St_Code_2001","Vill_Code_2001", 
                                      "Dst_Code_2001", "SubDist_Code_2001"),
                             duplicateGeoms = T)

#19. Uttar Pradesh 
Uttar_Pradesh <- sp::merge(`Uttar-Pradesh-Census2011-Boundaries.shp`, census_code_combined, by.x = c("sid","vill_code", "did", "tid"), 
                                   by.y = c("St_Code_2001","Vill_Code_2001", 
                                            "Dst_Code_2001", "SubDist_Code_2001"),
                                   duplicateGeoms = T)

#20. Uttarakhand
Uttarakhand <- sp::merge(`Uttarakhand-Census2011-Original-Boundaries.shp`, census_code_combined, by.x = c("sid","vill_code", "did", "tid"), 
                                 by.y = c("St_Code_2001","Vill_Code_2001", 
                                          "Dst_Code_2001", "SubDist_Code_2001"),
                                 duplicateGeoms = T)

#21 West Bengal 
West_Bengal <- sp::merge(`West-Bengal-Census2011-Boundaries.shp`, census_code_combined, by.x = c("sid","vill_code", "did", "tid"), 
                                 by.y = c("St_Code_2001","Vill_Code_2001", 
                                          "Dst_Code_2001", "SubDist_Code_2001"),
                                 duplicateGeoms = T)

#22 Maharashtra
#23 Madhya Pradesh 
#24 Chhatisgarh had files with 2011 census codes already.
#so no need to combine spatial data with directory info

#25. Manipur
Manipur_spatial = readOGR("C:\\Users\\pooja\\Documents\\GitHub\\Land-Tenure-Restoration-Potential\\Land-Tenure-Restoration-Potential\\Census2011-Original-BOundaries-From-Benjamin-data\\Manipur-Census2001-Original-Boundaries.shp")

Manipur_spatial <- sp::merge(Manipur_spatial, census_code_combined, by.x = c("SID","VILL_CODE", "DID", "TID"), by.y = c("St_Code_2001","Vill_Code_2001", "Dst_Code_2001", "SubDist_Code_2001"),duplicateGeoms = T)

#Save every state as a separate shapefile
writeOGR(obj = Andra_Pradesh, layer = "Andra_Pradesh", dsn= "Andhra-Pradesh-Census2011-Codes-Boundaries.shp", driver = "ESRI Shapefile")
writeOGR(obj = Assam, layer = "Assam", dsn= "Assam-Census2011-Codes-Boundaries.shp", driver = "ESRI Shapefile")
writeOGR(obj = Bihar, layer = "Bihar", dsn= "Bihar-Census2011-Codes-Boundaries.shp", driver = "ESRI Shapefile")
writeOGR(obj = Gujarat, layer = "Gujarat", dsn= "Gujarat-Census2011-Codes-Boundaries.shp", driver = "ESRI Shapefile")
writeOGR(obj = Haryana, layer = "Haryana", dsn= "Haryana-Census2011-Codes-Boundaries.shp", driver = "ESRI Shapefile")
writeOGR(obj = Himachal_Pradesh, layer = "Himachal_Pradesh", dsn= "Himachal-Pradesh-Census2011-Codes-Boundaries.shp", driver = "ESRI Shapefile")
writeOGR(obj = Jammu_Kashmir, layer = "Jammu_Kashmir", dsn= "Jammu-Kashmir-Census2011-Codes-Boundaries.shp", driver = "ESRI Shapefile")
writeOGR(obj = Jharkhand, layer = "Jharkhand", dsn= "Jharkhand-Census2011-Codes-Boundaries.shp", driver = "ESRI Shapefile")
writeOGR(obj = Karnataka, layer = "Karnataka", dsn= "Karnataka-Census2011-Codes-Boundaries.shp", driver = "ESRI Shapefile")
writeOGR(obj = Kerala, layer = "Kerala", dsn= "Kerala-Census2011-Codes-Boundaries.shp", driver = "ESRI Shapefile")
writeOGR(obj = Odisha, layer = "Odisha", dsn= "Odisha-Census2011-Codes-Boundaries.shp", driver = "ESRI Shapefile")
writeOGR(obj = Punjab, layer = "Punjab", dsn= "Punjab-Census2011-Codes-Boundaries.shp", driver = "ESRI Shapefile")
writeOGR(obj = Rajashthan, layer = "Rajashthan", dsn= "Rajasthan-Census2011-Codes-Boundaries.shp", driver = "ESRI Shapefile")
writeOGR(obj = Sikkim, layer = "Sikkim", dsn= "Sikkim-Census2011-Codes-Boundaries.shp", driver = "ESRI Shapefile")
writeOGR(obj = Tamil_Nadu, layer = "Tamil_Nadu", dsn= "Tamil-Nadu-Census2011-Codes-Boundaries.shp", driver = "ESRI Shapefile")
writeOGR(obj = Tripura, layer = "Tripura", dsn= "Tripura-Census2011-Codes-Boundaries.shp", driver = "ESRI Shapefile")
writeOGR(obj = Telangana, layer = "Telangana", dsn= "Telangana-Census2011-Codes-Boundaries.shp", driver = "ESRI Shapefile")
writeOGR(obj = Uttar_Pradesh, layer = "Uttar_Pradesh", dsn= "Uttar-Pradesh-Census2011-Codes-Boundaries.shp", driver = "ESRI Shapefile")
writeOGR(obj = Uttarakhand, layer = "Uttarakhand", dsn= "Uttarakhand-Census2011-Codes-Boundaries.shp", driver = "ESRI Shapefile")
writeOGR(obj = West_Bengal, layer = "West_Bengal", dsn= "West_Bengal-Census2011-Codes-Boundaries.shp", driver = "ESRI Shapefile")
writeOGR(obj = Manipur_spatial, layer = "Manipur_spatial", dsn= "Manipur-Census2011-Codes-Boundaries.shp", driver = "ESRI Shapefile")




```
