---
title: "People-centric restoration: Reporting district level results and figures"
author: "Pooja Choksi"
date: '2022-06-24'
output: html_document
---

USING THE DATA FROM PREVIOUS SCRIPT, CHUNKS OF CODE BELOW REPORT THE RESULTS AND FIGURES IN THE PAPER

```{r setup, include=FALSE}

library(data.table)
library(dplyr)
library(tidyr)
library(tools)
library(ggplot2)

```

Read in the data from previous script which has the districts ranked according to 
1. Climate vulnerability 
2. Total population 
3. MPI 
4. A combination of all variables 

It also has district level land tenure data

```{r message=FALSE, warning=FALSE, include=TRUE}

district_mpi_climate_summary = read.csv("District-Climate-MPI-Ranked.csv")

```

RESULTS TO REPORT IN THE PAPER 
We look at the top and bottom quantile of the mean rank of districts and discuss restoration methods which are appropriate for different land tenure regimes in more detail

1. CREATE THE DFS FOR TOP AND BOTTOM DISTRICTS 

```{r message=FALSE, warning=FALSE, include=TRUE}

#Determine the top and bottom quantile of districts 
summary(district_mpi_climate_summary$Mean_Rank_Scaled)

#1st q = 0.3221
#3rd q= 0.6429

top_districts = district_mpi_climate_summary%>%filter(Mean_Rank_Scaled<0.3221)

high_districts = district_mpi_climate_summary%>%filter(Mean_Rank_Scaled>0.6429)

middle_districts = district_mpi_climate_summary%>%filter(Mean_Rank_Scaled >0.3221 & Mean_Rank_Scaled<0.6429)

```

QUESTION 1: Which are the districts that should be prioritized when considering the following variables: (a) maximum population, (c) Multidimensional poverty index, (b) climate vulnerability index and (d) a combination of the variables?

PLOT OF THE STATES IN WHICH WE FIND THE TOP DISTRICTS 

```{r message= FALSE, warning=FALSE, include=TRUE}

#Which states make up the top quartile of districts? 
top_states = top_districts%>%group_by(State)%>%count()
  
#plot in descending order#assign order to prop variable
prop_order <-
  top_states%>%
  arrange(desc(n)) %>%
  mutate(State = factor(State))

topstates_plot = top_states%>%mutate(State = factor(State, levels = prop_order$State, ordered = TRUE))%>%ggplot(aes(x= State, y = n))+geom_col(aes(x=State), fill = "#440154FF")+theme_classic()+ theme(axis.text.x = element_text(angle = 45, hjust = 1))+
  labs(x = "State/ Union Territory", y = "Number of districts")

topstates_plot

```

QUESTION 2: Which land tenures within districts provide the largest number of hectares for restoration?

PLOT OF THE DISTRIBUTION OF EACH LAND TENURE IN THE TOP DISTRICTS AND REPORT % of LAND TENURE IN TOP DISTRICTS

```{r message=FALSE, warning=FALSE, include=TRUE}

#wide to long
top_district_long = reshape(top_districts, direction='long', varying=c('Total_Indiv_sum', 'Total_Common_sum', 'Total_Forest_sum', 'Total_Unaccounted_sum'), timevar= 'Land_Tenure', times=c('Individual', 'Common_NonForest', 'Forest', 'Unaccounted'),
v.names= 'Total_Hectares',
idvar=c('State', 'Total_Population_sum', 'X', "MPI_District", "Number_of_MPI_PeopleDistrict", "Living_standards", "MPI_rank", "Vulnerability_Rank", "Mean_Rank", "Mean_Rank_Scaled", "Total_hectares_for_prop_sum", "District_Name",
        "Total_Household_sum", "forests_land_sum", "non_agricultural_land_sum", "barren_uncultivable_land_sum", 
        "pasture_grazing_land_sum", "misc_tree_crop_land_sum",
        "culturable_wasteland_sum", "fallow_other_than_current_fallow_land_sum", "net_sown_area_sum", "current_fallow_land_sum", "total_irrigated_land_sum", "total_unirrigated_land_sum", "District_Code", "State_Code", 
        "Climate_vulnerability_index", "Combined_Rank"))

#plot of the distribution of land tenure in top districts
tenure_topdistricts = ggplot()+geom_histogram(data= top_districts, aes(x=Total_Forest_sum), fill ="#117733", alpha=0.5, binwidth = 300000)+geom_histogram(data = top_districts, aes(x=Total_Common_sum), fill = "#999933", alpha =0.5, binwidth = 300000)+ geom_histogram(data = top_districts, aes(x= Total_Indiv_sum), fill = "#E69F00", alpha= 0.5, binwidth = 300000)+ theme_classic()+ theme(axis.text.x = element_text(angle = 45, hjust = 1))+ labs(x = "Total number of hectares", y = "Freqeuncy")

tenure_topdistricts

#reporting % of land tenure in each district 
tenure_topdistricts_report = top_district_long%>%group_by(Land_Tenure)%>%summarise(hectares_category = sum(Total_Hectares))

tenure_topdistricts_report= tenure_topdistricts_report%>%mutate(tenure_total = colSums(tenure_topdistricts_report[,-1])) 

tenure_topdistricts_report = tenure_topdistricts_report%>%mutate(tenure_prop = (hectares_category/tenure_total)*100)

#see DF to report the distribution


##DISTRICT PLOT WITH SATURATION CURVES

#rearrange tenure common in descending order
top_dists_rearranged <- top_districts[order(top_districts$Total_hectares_for_prop_sum, decreasing=TRUE),]

#add cumulative column to the data frame
top_dists_rearranged[,"cum_indiv_hectares"] <- cumsum(top_dists_rearranged$Total_Indiv_sum)

top_dists_rearranged[,"cum_common_hectares"] <- cumsum(top_dists_rearranged$Total_Common_sum)

top_dists_rearranged[,"cum_forest_hectares"] <- cumsum(top_dists_rearranged$Total_Forest_sum)

top_dists_rearranged[,"cum_unaccounted_hectares"] <- cumsum(top_dists_rearranged$Total_Unaccounted_sum)

top_dists_rearranged[,"cum_total_population"] <- cumsum(top_dists_rearranged$Total_Population_sum)

#find duplicate district names
duplicated_districts = 
top_dists_rearranged[duplicated(top_dists_rearranged$District_Name), ]

#rename the duplicate districts to be able to plot in descending 
top_dists_rearranged = top_dists_rearranged%>%mutate(District_Name = case_when(District_Name == "Aurangabad" & State == "Bihar" ~ "Aurangabad_2", District_Name == "Bijapur" & State == "Karnataka" ~ "Bijapur_2", District_Name == "Bilaspur" & State == "Himachal Pradesh" ~ "Bilaspur_2", District_Name == "Hamirpur" & State== "Himachal Pradesh"~ "Hamirpur_2", District_Name == "Pratapgarh" & State == "Rajasthan" ~ "Pratapgarh_2", District_Name== "Raigarh" & State == "Maharashtra" ~ "Raigarh_2", District_Name == "Ranchi" & State == "Madhya Pradesh" ~ "Ranchi_2", TRUE ~ District_Name))

#plot in descending order#assign order to prop variable
prop_order <-
  top_dists_rearranged %>%
  arrange(desc(Total_hectares_for_prop_sum)) %>%
  mutate(District_Name = factor(District_Name))

#plot decreasing pop and cumulative hectares 
scaleRight = 20

topdistrict_tenure_curves  = top_dists_rearranged%>%mutate(District_Name = factor(District_Name, levels= prop_order$District_Name, ordered =TRUE))%>%
  ggplot(aes(x = District_Name, y = Total_hectares_for_prop_sum))+ 
  geom_col(aes(x = District_Name, y = Total_hectares_for_prop_sum, fill = State)) + 
    #geom_line(aes(x = State, y= cum_hectares, group = 1)) + 
 #geom_line(aes(y= cum_total_population/scaleRight), group = 1, color = "black", size = 1.2)+ 
  geom_line(aes(y= cum_indiv_hectares/scaleRight), group = 1, color = "#E69F00", size = 1.2)+ 
  geom_line(aes(y= cum_common_hectares/scaleRight), group = 1, color = "#999933", size = 1.2)+ 
  #geom_point(aes(y= cum_common_hectares/scaleRight), group = 1, color = "#999933")+ 
  geom_line(aes(y= cum_forest_hectares/scaleRight), group = 1, color = "#117733", size = 1.2)+ 
  #geom_point(aes(y= cum_forest_hectares/scaleRight), group = 1, color = "#117733")+
    scale_fill_manual(values = c(#"#aab539", 
      "#5b70dd", 
      #"#d2a035", 
      "#c13fa6", "#4fc271", "#d33680", "#4e8f2e", "#d27cde", "#41844a", "#dc375f", "#5dc3a3", "#b82d24", "#4ab4dd", "#e55744", "#517dc0", "#e37733", "#7956a3", "#9db269", "#a7487a", "#2e8871", "#cc5967", "#677328", "#a798e0", "#8c6d2c", "#db8ebb", "#a6572c", "#91567c", "#d79f66", "#9f494f", "#e3867c"))+ 
  scale_y_continuous(name = "Total hectares (in Millions)", labels = scales::label_number(unit = "M", scale = 1e-6))+
  theme_classic()+ theme(axis.title = element_text(size = 8), axis.text.x = element_blank(), axis.ticks.x = element_blank()) +theme(legend.position = "bottom")

topdistrict_tenure_curves

```
